\mytitle

### 2021-12-20 paper.tex
improve language

We find that the implementation presented in this paper and the
approach presented in Ref.~\cite{morris} (DILOG 0011) are fastest
among the ones shown in the table.  Both approaches use a rational
function approximant with the same number of terms.  However, the
approximant from Ref.~\cite{morris} has been implemented (for
comparison) to use Horner's scheme to evaluate the numerator and the
denominator.  Thus, the runtime difference of $\sim 30\%$ between
these two stems only from the fact that the implementation presented
in this paper uses Estrin's scheme to evaluate the numerator and the
denominator and as such can make use of ILP, while in the
implementation of Ref.~\cite{morris} the numerator and the denominator
must be evaluated sequentially.

>>>>

We find that the implementation presented in this paper and the
approach presented in Ref.~\cite{morris} (DILOG 0011) are fastest
among the ones shown in the table.  Both approaches use a rational
function approximant with the same number of terms.  However, the
approximant from Ref.~\cite{morris} has been implemented (for
comparison) to use Horner's scheme to evaluate the numerator and the
denominator.  Thus, the runtime difference of $\sim 30\%$ between
the two stems only from the fact that the implementation presented
in this paper uses Estrin's scheme to evaluate the numerator and the
denominator and as such can make use of ILP, while in the
implementation of Ref.~\cite{morris} the numerator and the denominator
must be evaluated sequentially.
